The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-03-17 paper/ms.tex
minor

>>>>

J.E. Forero-Romero acknowledges support from Vicerrector\'ia de
Investigaciones through a FAPA starting grant.

T. Verdugo acknowledges support from CONACYT through grant 165365 and
203489 through the program Estancias posdoctorales y sab\'aticas al
extranjero para la consolidaci\'on de grupos de investigaci\'on.
